\documentclass{article}

\usepackage{url}



\begin{document}
\title{CDT generator: Testing report}
\author{Pranav Kant Gaur}
\maketitle

\section{Objective}
This report documents the complete testing process adopted for verification and validation of the developed CDT generator.

\section{Testing PLY import and Export}
PLY reading/writing is performed using RPly\cite{rply} library. It was checked using reading a cube dataset as input and writing Delaunay tetrahedralization of vertices of cube as outout in a PLY file. Later, it was visualized using MeshLab and AnuVi to conform the vertices, faces and tetrahedrons were all written correctly back to PLY file.

\subsection{Issues}
Here are the issues faced/currently present in PLY reading writing:
\begin{enumerate}
	\item Some facets have vertices writen in \textit{clockwise} order, resulting in holes in the rendered tetrahedrlization. However, this also revealed bug in AnuVi which is rendering all facets regardless of their orientation.
		\subsubsection{Solution(s)}
		\begin{enumerate}
			\item Regarding vertex ordering in facet a query\cite{cgalForumMessage1} has been posted on CGAL forum.
		\item Mr. S. K. Bose is handling the issue of rendering on AnuVi.	
		\end{enumerate}

\end{enumerate}		




\begin{thebibliography}{1}
\bibitem{rply}
\url{http://w3.impa.br/~diego/software/rply/}	
\bibitem{cgalForumMessage1}
\url{http://cgal-discuss.949826.n4.nabble.com/Issue-in-visualizing-Delaunay-tetrahedralization-of-a-cube-td4660416.html}	

\end{thebibliography}

\end{document}
